
\addcontentsline{toc}{chapter}{Abstract}
%\chapter*{\begin{center}
%	{\normalsize Abstract}
%	\end{center}}
\chapter*{}
	\vspace*{-5cm}
%						{ {\large \textbf{Abstract}}
%							}
%							\\
							\begin{center}
								\textbf{Abstract}
							\end{center}
%\begin{abstract}
	
%	A long standing challenge in the areas of computer vision, image processing, and autonomous drive is to achieve high accuracy and real time performance. The real time performance in autonomous drive area makes to deploy its applications into autonomous car, navigation systems, etc. The computer vision and image processing when using in the field of defense and military demands for real time processing. One of the most prominent situations is to process the video data received at ground station from Unmanned Aerial Vehicle(UAV). The ground station will have a specific hardware and the data received should be processed in real time. The instantaneous results makes the authority at the ground station to take an immediate action on any intrusions in the area under surveillance.\paragraph*{}The demand to process the data in real time makes everybody to implement the algorithms effectively on to the target hardware. This is called the high performance implementations. The computer vision and image processing algorithms Adaptive contrast enhancement and motion de-blur are implemented on to a High performance system enabled with NVIDIA GPU. For the autonomous drive area an Embedded hardware powered by Rcar-H3 SiP is used. The autonomous algorithms temporal denoising, fog rectification are implemented to exploit the embedded hardware. As a special case to exploit the GPU based system, the stereo disparity algorithm is implemented on a system with NVIDIA GeForce GTX 1070 GPU. \paragraph*{}The data parallelism techniques are described for Adaptive contrast enhancement, motion deblur and stereo disparity algorithms and these algorithms are implemented on GPU enabled systems. For high performance implementation on to Embedded hardware, techniques like pipelining, divide and process are explained. The pipelining concept is used for fog rectification where as divide and process methodology is implemented for temporal denoising.
A long standing challenge in the areas of computer vision, image processing and autonomous drive systems is to achieve high accuracy with real time performance. It is very critical for applications deployed on autonomous vehicles to deliver results in real time, for not only meeting functional requirements, but also safety requirements. Any lapse in the performance of application can have catastrophic results. Hence, there is immense need to perform reliably at real time. Military and defense application areas also have critical needs for high performance applications. One of the most prominent situations in these contexts, is to process video data received at ground station from Unmanned Aerial Vehicle (UAV). The ground station will have scope of hosting high performance hardware that can be used to exploit the received data for making immediate intelligent decisions. These demands to process the data in real time requires efficient implementation of algorithms on to the target hardware. \paragraph*{}This thesis focuses on high performance implementations of key computer vision and image processing algorithms. These algorithms are chosen such that both the areas of autonomous vehicles and UAV based applications are covered. Adaptive contrast enhancement and Motion de-blur are the chosen applications that are implemented on a High performance hardware server used in ground stations that exploit UAV data. The high performance hardware here consists of multiple processing elements like Single Board Computer (SBC), GPU, DSP \& FPGA. This work exploits SBC and GPU for implementing these applications using concepts of data parallelism and memory optimizations.
\paragraph*{}In the autonomous drive area, there are more challenges to make the applications run on an Embedded hardware with limited resources both in terms of computation and memory. In this work, applications are developed that exploit pipelining, parallel processing and task based parallelism techniques. Autonomous SOCs used for testing these applications are Renesas based Rcar-H3 SiP and nVidia’s Tegra X1 SoC. Fog rectification, temporal denoising and stereo disparity applications are implemented to exploit these embedded hardware. To further understand and exploit the usage of GPU, Stereo disparity application is implemented using parallel GPU streams. \paragraph*{}This thesis focuses on the design and implementation of these image processing and computer vision applications. Performance analysis is done for each of the algorithms and achieved speedups are reported. The speedups range from 1.5X to 9X depending on the kind of application and employed performance techniques.
%\end{abstract}
%\end{abstract}	