\addcontentsline{toc}{chapter}{Bibliography}
\begin{thebibliography}{9}
\bibitem{ACE} 
Tsai, Chun-Ming, and Zong-Mu Yeh. "Contrast enhancement by automatic and parameter-free piecewise linear transformation for color images." IEEE Transactions on Consumer Electronics 54.2 (2008): 213-219.  
\bibitem{Blurred image restoration}
Dobes, Michal, Libor Machala, and Tomas First. "Blurred image restoration: A fast method of finding the motion length and angle." Digital Signal Processing 20.6 (2010): 1677-1686.
\bibitem{motion blur estimation} Tiwari, Shamik, et al. "Review of motion blur estimation techniques." Journal of Image and Graphics 1.4 (2013): 176-184.
\bibitem{Professional CUDA}Professional CUDA C Programming by John Cheng, Max Grossman, and Ty McKercher.
\bibitem{fog removal}“Single image fog removal using anisotropic diffusion” A.K. Tripathi S. Mukhopadhyay, IET Image Process., 2012, Vol. 6, Iss. 7, pp.
\bibitem{dehaze}Schechner, Y.Y., Narasimhan, S.G., Nayar, S.K.: ‘Instant dehazing of images using polarization’. IEEE Computer Society Conf. on Computer Vision and Pattern Recognition, 2001, pp. 325– 332
\bibitem{fastvis}Tarel, J.P., Hautiere, N.: ‘Fast visibility restoration from a single color or gray level image’. IEEE Int. Conf. on Computer Vision, 2009, pp. 2201– 2208
\bibitem{ChrFramework} Narasimhan, S.G., Nayar, S.K.: ‘Chromatic framework for vision in bad weather’. IEEE Conf. on Computer Vision and Pattern Recognition, 2000, vol. 1, pp. 598–605
\bibitem{anisotropic} Perona, P., Malik, J.: ‘Scale space and edge detection using anisotropic diffusion’, IEEE Trans. Pattern Anal. Mach. Intell., 1990, 12, (7), pp. 629–639
\bibitem{hazeremo} He, K., Sun, J., Tang, X.: ‘Single image haze removal using dark channel prior’. IEEE Int. Conf. on Computer Vision and Pattern
Recognition, 2009, pp. 1956–1963
\bibitem{alan-tatourian}https://tatourian.blog/2013/09/03/nvidia-gpu-architecture-cuda-programming-environment/
\bibitem{flynn}https://en.wikipedia.org/wiki/Flynn\%27s\_taxonomy
\bibitem{amd}http://developer.amd.com/resources/heterogeneous-computing/what-is-heterogeneous-computing/
\bibitem{apod}http://docs.nvidia.com/cuda/cuda-c-best-practices-guide/\#assess-parallelize-optimize-deploy
\end{thebibliography}